Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2025-07-25 Edith Zemanick/Sweat Variability/sweat_test_analysis.qmd
removing sweat Cl > 160
fixed ROC labels

# Change Cl under 10 to missing

@@

@@

```{r}
plot(roc_list[[2]],
  print.auc = T, print.thres = T,
  main = "Cystic Fibrosis vs. Non-CF"
)
plot(roc_list[[1]],
  print.auc = T, print.thres = T,
  main = "CFTR-RD or CRMS vs. Cystic Fibrosis"
)
plot(roc_list[[3]],
  print.auc = T, print.thres = T,
  main = "CFTR-RD or CRMS vs. Non-CF"
)
```

>>>>

# Change Cl under 10 or over 160 to missing

@@

df$Cl[df$Cl > 160] <- NA
# Remove Na under 10 as well

@@

```{r}
plot(roc_list[[2]],
  print.auc = T, print.thres = T,
  main = "Cystic Fibrosis vs. CFTR-RD or CRMS"
)
plot(roc_list[[1]],
  print.auc = T, print.thres = T,
  main = "Cystic Fibrosis vs. Non-CF"
)
plot(roc_list[[3]],
  print.auc = T, print.thres = T,
  main = "CFTR-RD or CRMS vs. Non-CF"
)
```
